D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-03 ootavacuous.tex
Alan Stern review December 3rd
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\paragraph{Omitted Redundant Atomic Stores}
In contrast, a pair of back-to-back non-volatile atomic stores to \co{x}
might always be executed such that no other thread accesses \co{x}
during the time between those two stores.
This means that, short of inspecting the assembly code, the user has no
way of proving that the C++ implementation acted as if that store was
omitted from the source code.
In cases where this is undesirable, the user can resort to volatile
atomic stores or to inline assembly\footnote{
	For example, by placing the Linux-kernel \co{barrier()} macro
	between the two stores.
	This macro is an empty GCC \co{asm} that specifies the \co{memory}
	clobber.}
to prevent the compiler from omitting a store.
However, acting as if such a redundant store was omitted from the source
code cannot create an OOTA cycle.
After all, the implementation is already within its as-if rights to
assume that the first of a back-to-back pair of non-volatile relaxed
atomic stores was omitted from the source code.

>>>>

\paragraph{Omitted Redundant Atomic Stores}
In contrast, a pair of back-to-back non-volatile atomic stores to \co{x}
might always be executed such that no other thread accesses \co{x}
during the time between those two stores.
This means that, short of inspecting the assembly code, the user has no
way of proving that the C++ implementation acted as if that store was
omitted from the source code.
In cases where this omission is undesirable, the user can resort to
volatile atomic stores or to inline assembly\footnote{
	For example, by placing the Linux-kernel \co{barrier()} macro
	between the two stores.
	This macro is an empty GCC \co{asm} that specifies the \co{memory}
	clobber.}
to prevent the compiler from omitting a store.
However, acting as if such a redundant store was omitted from the source
code cannot create an OOTA cycle because any valid execution (OOTA or not)
of the program with the first of a back-to-back pair of non-volatile
relaxed atomic stores omitted is essentially a valid execution of the
program with the store present.
